Runaway and hypervelocity stars from binary-single encounters in globular clusters

### 2022-10-14 src/tex/ms.tex
Refined v_los cdf, and added pdf.  Also made all scripts dependent on rustics.py
Added Spitzer reference.

In the interest of predicting realistic statistics and rates for a MW-like GC population, we assign representative \CMC\ models to each of the GCs in an aggregate observational catalog.
The 148 models in the \CMCcat\ are specified by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
After the same paper we use cluster mass $M$ and core radius to half-mass radius ratio $r_{\rm core} / r_{h,m}$ to relate \CMC\ models to MW GCs, and in this study we also include metallicity $Z$ to help distinguish otherwise similar systems.
We use the definition of core radius from [CITATION, the Spitzer book?]:
\begin{equation}
    r_{\rm core} = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
\end{equation}
where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster.

@@

>>>>

In the interest of predicting realistic statistics and rates for a MW-like GC population, we assign representative \CMC\ models to each of the GCs in an aggregate observational catalog.
The 148 models in the \CMCcat\ are specified by cluster initial size $N$ (number of stellar objects), initial virial radius $r_{\rm vir}$ (parsecs), distance from the galactic center $r_{\rm gc}$ (kiloparsecs, used in \CMC\ to calculate tidal effects from the galactic potential), and metallicity $Z$ (used to prescribe star evolution), with values chosen to span much of the MW GC parameter space; see \citet{2020IAUS..351..357K} for more details.
After the same paper we use cluster mass $M$ and core radius to half-mass radius ratio $r_{\rm core} / r_{h,m}$ to relate \CMC\ models to MW GCs, and in this study we also include metallicity $Z$ to help distinguish otherwise similar systems.
We use the definition of core radius from \citet{1987degc.book.....S}:
\begin{equation}
    r_{\rm core} = \sqrt{\frac{3 \sigma_c^2}{4 \pi \rho_c}},
\end{equation}
where $\sigma_c$ is the central velocity dispersion and $\rho_c$ is the central density for the cluster.

@@

\begin{figure}[ht!]
    \script{cmc_orbits_pdf.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cmc_orbits_pdf_S.pdf}
        \caption{
            Plot showing orbit pdf.  $v_{\rm los}$ is the radial velocity measured on earth transformed to the galactic rest frame.
        }
        \label{fig:cmc_orbits_pdf}
    \end{centering}
\end{figure}
